%! TEX root=../main.tex

\subsection{Response 2}
  \begin{quotation}
    My favorite form of conflict resolution is collaboration. It is rarely used
      systematically in society itself, but it is incredible in the workplace.
      In collaboration we build relationships with other people and utilize
      the strengths and weaknesses of one another. The team uses partners from
      outside the collaboration such as industry partners to make a powerful
      decision the team can have all individual inputs.

    Collaboration can be effective because the return on investment in time can
      be maximized. In a good collaboration there is a massive amount of
      research and discussion completed. There should not be a lot of voting
      because that will limit the decision making.

    In the current situation with COVID-19 where colleagues and team members
      are in completely different physical locations at an unprecedented level,
      it is even more essential to build collaborative skills to solve conflict.
  \end{quotation}

  \paragraph{This is a response to Cherylee Parker on Post ID 43279232}
    Interesting analysis, Cherylee! I agree with you on the fact that
      collaboration is important in a workplace environment. Have you ever been
      a part of a workplace environment where collaboration is difficult, if
      not impossible, with your fellow coworkers (or, usually, management)?
      I know I personally have, and perhaps that is why I find work to be an
      even more difficult place to maintain solid foundations of conflict
      resolution when you just \textit{know} you are the one in the right. Have
      you any tips/tricks/techniques to get around this in your own experience?
