\documentclass[stu,12pt]{apa7}
  \usepackage{times}               % Times New Roman Font Face
  \usepackage[american]{babel}      % Localization
  \usepackage[utf8]{inputenc}      % Input Encoding
  \usepackage{hyperref}            % Hyperlinks
  \usepackage{enumitem}            % Additional Enumeration Environment Settings
  \usepackage{geometry}            % Page Layout
  \usepackage{soul}                % Text Highlighting
  \usepackage{graphicx}            % Images
  \usepackage{csquotes}            % Quoting Environment
  \usepackage{bookmark}            % Required by `csquotes'
  \usepackage{mdframed}            % Colorful Tex-Box Environment
  \usepackage[toc]{appendix}       % Appendix
  \usepackage{fancyhdr}            % Headings and Footers
  \usepackage[%
    style=apa,%
    sortcites=true,%
    sorting=nyt%
  ]{biblatex}
  \usepackage{xcolor}

  % Bibliography Setup
  %% Language Mappings
  \DeclareLanguageMapping{english}{english-apa}
  \DeclareLanguageMapping{american}{american-apa}
  %% Bibliography File Path
  \addbibresource{main.bib}
  %% Categories for Specified Bibliography Items
  %%% Category for sources not referenced in-text
  \DeclareBibliographyCategory{consulted}
  \addtocategory{consulted}{noauthor_communication_2013}
  \addtocategory{consulted}{noauthor_business_nodate}
  \addtocategory{consulted}{noauthor_college_nodate}
  \addtocategory{consulted}{thomas_exploration_2020}
  \addtocategory{consulted}{noauthor_he_nodate}
  \addtocategory{consulted}{reed_leaving_2006}
  \addtocategory{consulted}{bacha_how_2016}


  % Hyperlink Setup
  \hypersetup{
    colorlinks = true,
    urlcolor = blue,
    linkcolor = blue,
    citecolor = blue
  }

  % Page and Text Layout
  \geometry{%
    a4paper,%
    top=1in,%
    bottom=1in,%
    left=1in,%
    right=1in%
  }
  \setlength{\headheight}{15pt}

  % Header
  \lhead{COM120CG1-M2D1}

  % Title Page
  \title{%
    M2D1: Fight or Flight
  }
  \shorttitle{Module 2 Discussion 1}
  \author{Ashton Hellwig}
  \authorsaffiliations{Department of Mathematics, Front Range Community College}
  \course{COM115: Interpersonal Communication}
  \professor{Richard Thomas}
  \duedate{November 14, 2020 23:59:59 MDT}
  \date{\today}
  \abstract{%
    \textbf{Overview}\\%
    We all deal with conflict differently. Some of us avoid an argument, while
      others escalate it. Perhaps you are willing to compromise, or maybe you
      would rather compete. As we saw in the movie clip, having different
      conflict resolution styles can make it very hard to reach an agreement.
      Even if you never change your conflict resolution method, being able to
      identify its strengths and weaknesses will help you become a better
      communicator.\\%

    You should spend approximately 4 hours on this assignment.%
  }

\begin{document}
  % Title Page
  \maketitle

  % Initial Post
  \section{Initial Post}
    \subsection*{Instructions}
      \begin{enumerate}
        \item Be sure you have completed your readings and explored all the
          materials, including videos, in the Exploration page accessible within
          the ``Read/View'' topic of Module 2 Content.
        \item In the video appearing within the topic titled, ``Gender and
          Conflict'' we saw that Brooke and Gary had two very different ways of
          dealing with conflict, which caused a small disagreement to escalate
          into a huge argument.
        \item Click on the ``CR Kit'' Word Document link appearing on the fourth
          topic titled ``Improving Your Skills'' which is listed within
          ``Exploration of He Said! She Said'' under ``Read/Review''. Next,
          review the self-assessment content to determine your personal conflict
          resolution method (style).
          \begin{itemize}
            \item \textbf{NOTE}: There is NOT an assessment for you to complete.
              Again, REVIEW the self-assessment CONTENT to determine your
              personal conflict resolution method (style). If you find yourself
              equally split between two or more methods, then choose the one you
              feel is most important to you.
          \end{itemize}
        \item Conduct research of the conflict resolution method (style) you
          selected. For example what are the pros and cons of the conflict
          resolution method (style) based on your research?
      \end{enumerate}


      % My Conflict Resolution Method/Style
      \newpage
      \paragraph{My Conflict Resolution Method: Empathy}
        The conflict resolution method I tend to lean towards the most would
          have to be that of empathy. Empathy goes a \textit{long} way when
          resolving conflict. Many times throughout the duration of an argument,
          one party may not be feeling \emph{heard}. The main theme in empathy
          is a high degree of being able to understand the other party's
          feelings, and allowing them to feel heard
          \parencite[pp. 48]{wied_empathy_2007}. Empathy is not only a
          pleasurable experience for the speaker due to a feeling of
          understanding, but also for the listener as it can allow them to see
          the conflict from another point of view, leading to a quicker conflict
          resolution timeline \parencite[pp. 49]{wied_empathy_2007}.

      % The Pitfalls of Empathy
      \paragraph{The Pitfalls of Empathy}
        While empathy does tend to be a safe route to take in terms of conflict
          resolution, there are a few negatives to having a high degree of
          empathy. ``Empaths'' (Those with a high degree of empathy) can be
          overwhelmed in situations of intense emotion and even actually
          \textit{feel} the other person's pain
          \parencite[pp. 376]{schieman_when_2001}. Sometimes, this could be
          interpreted by the other individual as a way for the listener to
          ``make a situation about them'', rather than associating physical
          empathy with sympathy. Furthermore, those with a higher level of
          empathy tend to also have higher instances of symptoms of depression
          \parencite[pp. 376]{schieman_when_2001}. Finally, empathy is a hard
          metric for one to measure, as there are a multitude of systems
          designed for the academic reporting of empathy in academic studies
          \parencite[pp. 675]{zaki_neuroscience_2012}.


  % Replies
  \include{tex/01-response.tex}
  % \include{tex/02-response.tex}

  % Bibliography
  %% Works Cited
  \newpage
  \printbibliography[%
    title={References},%
    heading={bibintoc},%
    notcategory={consulted}%
  ]

  %% Works Consulted
  \newpage
  \nocite{*}
  \printbibliography[%
    title={Additional References},%
    heading={bibintoc},%
    category={consulted}%
  ]
\end{document}
